% \documentclass[PhD]{nitgoathesis}
%\documentclass[MTech]{nitgoathesis}
\documentclass[BTech]{nitgoathesis}
\usepackage{times}
 \usepackage{t1enc}

\usepackage{graphicx}
\usepackage{epstopdf}
%\usepackage[hypertex]{hyperref} % hyperlinks for references.
\usepackage{amsmath} % easier math formulae, align, subequations \ldots

\begin{document}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Title page

\title{ NAME OF THE DISSERTATION TO BE ENTERED}

\author{Krithika  \vspace{10pt} (10CS009)}
\author{Krithika  \vspace{10pt} (10CS009)}
\author{Krithika  \vspace{10pt} (10CS009)}
\author{Krithika  \vspace{10pt} (10CS009)}

\date{MONTH 2014}
\department{COMPUTER SCIENCE AND ENGINEERING}

%\nocite{*}
\maketitle

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Certificate
\certificate

\vspace*{0.5in}

\noindent This is to certify that the work contained in this Dissertation entitled ``Name of the Dissertation Title is to be Entere'' 
submitted by the group members Mr. XXXXXX (Roll. No: XXXXXXXXX), Mr. XXXXXXX (Roll No: XXXXXX) and Mr. XXXXXX, (Roll. No: XXXXXX) to the 
Department of Computer Science and Engineering, National Institute of Technology Goa, for the partial fulfilment of the requirements for 
the degree of Bachelor of Technology in Computer Science and Engineering. They have carried out their research work under my 
supervision. This work has not been submitted else- where for the award of any other degree or diploma.\newline
\noindent The Dissertation, in my opinion, has reached the standard fulfilling of the requirements for the degree of Bachelor of 
Technology in Computer Science and Engineering in accordance with the regulations of the Institute.

\vspace*{1.5in}

\begin{singlespacing}
\hspace*{2.8in}
\parbox{3in}{
\noindent {Name of the Guide} \\
\noindent Designation \\ 
\noindent Department Name \\
\noindent National Institute of Technology Goa-403401\\
\noindent  \\
} 
% \hspace*{2.8in}
% \parbox{3in}{
% \noindent {Name of the Guide} \\
% \noindent Designation \\ 
% \noindent Department Name \\
% \noindent National Institute of Technology Goa-403401\\
% \noindent  \\
% } 
\end{singlespacing}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Acknowledgements
\acknowledgements

Thanks to all those who made \TeX\ and \LaTeX\ what it is today.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Abstract

\abstract

% \noindent KEYWORDS: \hspace*{0.5em} \parbox[t]{4.4in}{\LaTeX ; Thesis;
%   Style files; Format.}

% \vspace*{24pt}
% 
 \noindent  A \LaTeX\ class along with a simple template thesis are
provided here.  These can be used to easily write a thesis suitable
for submission at NIT Goa.  The class provides options to format
PhD, M.Tech.\ and B.Tech.\ thesis.  It also allows one to write a
synopsis using the same class file.  Also provided is a BIB\TeX\ style
file that formats all bibliography entries as per the IEEE format.

The formatting is as  per the current
institute guidelines.

\pagebreak

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Table of contents etc.

\begin{singlespace}
\tableofcontents
\thispagestyle{empty}

\listoftables
\addcontentsline{toc}{chapter}{List of Tables}
\listoffigures
\addcontentsline{toc}{chapter}{List of Figures}
\end{singlespace}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Abbreviations
\abbreviations

\noindent 
\begin{tabbing}
xxxxxxxxxxx \= xxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxx \kill
\textbf{NITG}   \> National Institute of Technology Goa \\
\textbf{RTFM} \> Read the Fine Manual \\
\end{tabbing}

\pagebreak

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Notation

\chapter*{\centerline{NOTATION}}
\addcontentsline{toc}{chapter}{NOTATION}

\begin{singlespace}
\begin{tabbing}
xxxxxxxxxxx \= xxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxx \kill
\textbf{$r$}  \> Radius, $m$ \\
\textbf{$\alpha$}  \> Angle of thesis in degrees \\
\textbf{$\beta$}   \> Flight path in degrees \\
\end{tabbing}
\end{singlespace}

\pagebreak
\clearpage

% The main text will follow from this point so set the page numbering
% to arabic from here on.
\pagenumbering{arabic}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Introduction.

\chapter{INTRODUCTION}
\label{chap:intro}
\section{Sections}
This is how you have to write citation \cite{DBLP:journals/tit/IngemarssonTW82}
\appendix

\chapter{A SAMPLE APPENDIX}

Just put in text as you would into any chapter with sections and
whatnot.  Thats the end of it.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Bibliography.

\begin{singlespace}
  \bibliography{Sai-myfile}
\end{singlespace}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% List of papers

% \listofpapers

% \begin{enumerate}  
% \item Authors....  \newblock
%  Title...
%   \newblock {\em Journal}, Volume,
%   Page, (year).
% \end{enumerate}  

\end{document}
